A Lattice Boltzmann Method for immiscible multiphase flow simulations using the Level Set Method

### 2015-08-12 Vortrag/folien.tex
Performance optimiert.. Objektorientierung ist quatsch..
ian-mitchel-toolbox heruntergeladen + folien erweitert

\documentclass[ucs]{beamer}

@@

I.e. a \textit{level set function} $\phi:= \phi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given by the zero-isosurface of this function.
It holds
$$ \frac{\partial \phi}{\partial t} + \vec v \cdot \nabla \phi = 0$$
%todo benefits erklaeren
\end{frame}

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Interface capturing}
Level-Set function only stored in narrow band around interface, Adalsteinsson and Sethian

@@

@@

>>>>

\documentclass[ucs]{beamer}
\usepackage{etex}

@@

I.e. a \textit{level set function} $\phi:= \phi(x,t) \rightarrow \mathbb{R}$ is tracked through the fluid domain. The interface is given by the zero-isosurface of this function.
It holds:
$$ \frac{\partial \phi}{\partial t} + \vec v \cdot \nabla \phi = 0.$$
%todo benefits erklaeren
\end{frame}

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Interface capturing}
Level-Set function only stored in narrow band around interface, Adalsteinsson and Sethian
TODO: Quellen als Footnotes + Uebersichtsfolie

@@

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Level Set}
\begin{itemize}
\item<1-> The level set equation of Osher and Sethian
 $$\varphi_t+v \cdot \nabla \varphi = 0$$
\item<2-> with the level set function $\varphi$
\item<3-> we will use the signed distance function as level set function and therefore we get
$$n = \nabla \varphi$$
$$\kappa = \nabla \varphi$$
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Coupling of LBM and level set method}
\begin{itemize}
\item<1-> New boundary condition at the interface
$$f_i(x,t+1) = f_{i^*}^{+}(x,t) + 6hf_{i}^{*}c_i \cdot \tilde{u} + R_i$$
\end{itemize}
\end{frame}
